The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-04-13 RET_Hosts_SNWG.tex

{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best\tnote{a} &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\

@@

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion factors given in \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale. Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the PDFs of the various different diagnostics scaled to PP04 O3N2, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.

>>>>

{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(\mathrm{yr}^{-1} \right)$& Best\tnote{a} &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\

@@

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion factors given in \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale. Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the PDFs of the various different diagnostics scaled to PP04 O3N2, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16\textsuperscript{th} and 84\textsuperscript{th} percentiles of these PDFs, and for DES RETs display the results in Table \ref{tab:derived}.
